### 2010-02-01 trunk/deliverables/D4_3_2/fast_d4_3_2.tex
Added some related work.
git-svn-id: https://svn.forge.morfeo-project.org/fast-fp7project@493 d8b0c59b-6544-0410-94d9-83a5658a058e

>>>>

The rule based approach of the service wrapper tool has been inspired by triple graph grammars, cf. \cite{conf/wg/Schurr94,JSZ97c}. While general triple graph grammars allow to relate complex graph structures with each other, in our case the target of a rule is always a single object or attribute. This facilitates the whole mechanism, reasonably.
